The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
add raster cite

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 10m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
<!-- TODO: "foraging" should be "lichen" ?--> consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.
<!-- TODO: cite the raster package for R? -->

>>>>

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 10m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R package `raster` [@Hijmans_2019]. Foraging habitat
<!-- TODO: "foraging" should be "lichen" ?--> consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.
